Mode and tempo of promoter evolution as observed in the \textit{Paramecium aurelia} species complex

### 2019-03-12 manuscript.tex
Updates from Overleaf

\title{Mode and tempo of promoter evolution as measured in the \textit{Paramecium aurelia} species complex}

@@

\address{$^{1}$Biodesign Center for the Mechanisms of Evolution\\
$^{2}$School of Life Sciences\\
Arizona State University, 797 E. Tyler Street, Tempe, AZ 85281}

@@

\keyword{cis-regulatory regions, duplicate genes, paralogous genes, Paramecium, promoter evolution, TSS profiling.}

>>>>

\title{Mode and tempo of promoter evolution as observed in the \textit{Paramecium aurelia} species complex}

@@

\address{$^{1}$Biodesign Institute Center for the Mechanisms of Evolution\\
$^{2}$School of Life Sciences\\
Arizona State University, 797 E. Tyler Street, Tempe, AZ 85281}

@@

\keyword{\textit{cis}-regulatory regions, gene duplicates, paralogous genes, Paramecium, promoter evolution, TSS profiling.}
